On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-25 5_Threats.tex
minor review

Construct validity is connected with how well the selected measures actually represent the concept of interest. We use correctness as a proxy for program comprehension. Furthermore, we use predicted outcomes of small programs as a measure of correctness. As discussed elsewhere~\cite{Oliveira:2020:ECR}, this approach is a test of the developers' ability to trace programs. Although this is a common approach in studies about atoms of confusion~\cite{TheEyesDoNotLie,Langhout:2021:ACJ,DBLP:conf/sigsoft/GopsteinIYDZYC17}, other measures of correctness could have been employed, potentially yielding different results. As a complement to correctness in the survey, we have measured the time it took for the participants to finish. Furthermore, we have  asked the interviewees about their preferences when comparing confusing and clean versions of the programs.

>>>>

Construct validity is connected with how well the selected measures actually represent the concept of interest. We use correctness as a proxy for program comprehension. Furthermore, we use predicted outcomes of small programs as a measure of correctness. As discussed elsewhere~\cite{Oliveira:2020:ECR}, this approach is a test of the developers' ability to trace programs. Although this is a common approach in studies about atoms of confusion~\cite{TheEyesDoNotLie,Langhout:2021:ACJ,DBLP:conf/sigsoft/GopsteinIYDZYC17}, other measures of correctness could have been employed, potentially yielding different results. As a complement to correctness in the survey, we have measured the time it took for the participants to correctly predict the outcome of the code snippets (either with or without atom candidates). Furthermore, we have  asked the interviewees about their preferences when comparing confusing and clean versions of the programs.
